Data preprocessing: raw data to processed data

### 2023-03-23 README.Rmd
updated manuscript based on contributor feedback and restructured the folders to deploy the interactive plot

@@

The `manuscript/` folder contains the manuscript and supplementary materials documents with the analysis code embedded in them. The folder also includes the `interactive_report.Rmd` file, which includes an interactive document for reanalyzing our results with different subsets of the data. To run the interactive document locally on your computer, click the _Run document_ button in Rstudio or run the `rmarkdown::run(here::here("manuscript/interactive_report.Rmd"))` function in your R console. The `figs/` subfolder contains the rendered figures from the manuscript and supplementary materials in .pdf and .png formats.

>>>>

The `root` folder includes the `interactive_report.Rmd` file, which includes an interactive document for reanalyzing our results with different subsets of the data. To run the interactive document locally on your computer, click the _Run document_ button in Rstudio or run the `rmarkdown::run("interactive_report.Rmd")` function in your R console.

@@

The `manuscript/` folder contains the manuscript and supplementary materials documents with the analysis code embedded in them. The `figs/` subfolder contains the rendered figures from the manuscript and supplementary materials in .pdf and .png formats.

### 2023-03-23 interactive_report.Rmd
updated manuscript based on contributor feedback and restructured the folders to deploy the interactive plot

---
title: "Results exploration"
output: html_document
runtime: shiny
---

@@

# Create figure
renderPlot({
  plot(alspac_plot_likert_data(), digits = 1, ordered = TRUE, group.order = names(alspac_plot_data()), text.size = 5.5) +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 25), limits = rev(names(alspac_plot_data))) +
    labs(title = str_wrap("Thinking about a study you may run with ALSPAC data (or one that you have recently run)..."), width = 25) +
    theme(
      axis.title.x = element_blank(),
      title = element_text(size = 14),
      axis.text.y = element_text(size = 14),
      axis.text.x = element_text(size = 16),
      legend.text = element_text(size = 15),
      legend.title = element_blank(),
      plot.margin = margin(t = 0, r = 0, b = 3.5, l = 0, unit = "lines"),
      legend.position = c(.35,-.2),
      legend.direction = "horizontal"
    )
})
```

>>>>

---
title: "Results exploration"
output: html_document
runtime: shiny
resource_files:
- R/utils.R
---

@@

# Create figure
renderPlot({
  plot(alspac_plot_likert_data(), digits = 1, text.size = 5.5) +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 25), limits = rev(names(alspac_plot_data()))) +
    labs(title = str_wrap("Thinking about a study you may run with ALSPAC data (or one that you have recently run)..."), width = 25) +
    theme(
      axis.title.x = element_blank(),
      title = element_text(size = 14),
      axis.text.y = element_text(size = 14),
      axis.text.x = element_text(size = 16),
      legend.text = element_text(size = 15),
      legend.title = element_blank(),
      plot.margin = margin(t = 0, r = 0, b = 3.5, l = 0, unit = "lines"),
      legend.position = c(.35,-.2),
      legend.direction = "horizontal"
    )
})
```

### 2023-03-23 manuscript/manuscript.Rmd
updated manuscript based on contributor feedback and restructured the folders to deploy the interactive plot

```{r typicallyEcawPlot, warning=FALSE, fig.cap="Caption goes here...", fig.align="center", out.width="100%", fig.width=12.8, fig.height=6, fig.path='figs/', dev=c('png', 'pdf')}
# Create typically trustworthy and reproducible plot
# Check if there is any missing and don't understand responses separately
# processed %>%
#   select(contains("typically_")) %>%
#   dplyr::filter(is.na(typically_reproducible) | is.na(typically_trustworthy) | typically_reproducible == "I don't understand the question" | typically_trustworthy == "I don't understand the question") %>%
#   nrow()

@@

# Create ecaw trustworthy and reproducible plot
# Calculate missing responses
ecaw_missing_text <-
  processed %>%
  select(contains("ecaw_")) %>%
  pivot_longer(
    cols = everything(),
    names_to = "item",
    values_to = "value"
  ) %>%
  dplyr::filter(is.na(value) | value == "I don't understand the question") %>%
  mutate(item = str_to_title(str_remove(item, "^[^_]*_"))) %>%
  replace_na(list(value = "Missing")) %>%
  group_by(item, value) %>%
  summarise(
    n = n()
  ) %>%
  ungroup() %>%
  mutate(text = paste(value, "=", n))

@@

Respondents generally agreed that studies that analyze preexisting observational datasets are trustworthy[^3] (`r pull(filter(typically_trustworthy, support == "positive"), percentage)`%) and reproducible[^4] (`r pull(filter(typically_reproducible, support == "positive"), percentage)`%) (Figure 1A). At the same time, many agreed that a study using an ECAW would be _more_ trustworthy (`r pull(filter(ecaw_trustworthy, support == "positive"), percentage)`%) and _more_ reproducible (`r pull(filter(ecaw_reproducible, support == "positive"), percentage)`%) compared to a typical study using preexisting observational data (Figure 1B).

```{r methodDescriptives, include=FALSE}
confirmatory <- level_percentage(
  processed,
  method_confirmatory,
  c(
    "Never or almost never",
    "Sometimes",
    "About half the time",
    "Most of the time",
    "Always or almost always"
  ),
  "I don't understand the question"
) %>%
  filter(method_confirmatory != "Never or almost never") %>%
  summarise(sum_percentage = sum(percentage)) %>%
  pull(sum_percentage)

exploratory <- level_percentage(
  processed,
  method_exploratory,
  c(
    "Never or almost never",
    "Sometimes",
    "About half the time",
    "Most of the time",
    "Always or almost always"
  ),
  "I don't understand the question"
) %>%
  dplyr::filter(method_exploratory != "Never or almost never") %>%
  summarise(sum_percentage = sum(percentage)) %>%
  pull(sum_percentage)

preregistered <- level_percentage(
  processed,
  method_preregistered,
  c(
    "Never or almost never",
    "Sometimes",
    "About half the time",
    "Most of the time",
    "Always or almost always"
  ),
  "I don't understand the question"
)

blind <- level_percentage(
  processed,
  method_blind,
  c(
    "Never or almost never",
    "Sometimes",
    "About half the time",
    "Most of the time",
    "Always or almost always"
  ),
  "I don't understand the question"
)

script <- level_percentage(
  processed,
  method_script,
  c(
    "Never or almost never",
    "Sometimes",
    "About half the time",
    "Most of the time",
    "Always or almost always"
  ),
  "I don't understand the question"
)
```

Over half of respondents reported that their studies using preexisting observational data are preregistered never or almost never (`r filter(preregistered, method_preregistered == "Never or almost never") %>% pull(percentage)`%), or sometimes (`r filter(preregistered, method_preregistered == "Sometimes") %>% pull(percentage)`%) (Figure 2A). About half reported sharing their analysis scripts never or almost never (`r filter(script, method_script == "Never or almost never") %>% pull(percentage)`%), or sometimes (`r filter(script, method_script == "Sometimes") %>% pull(percentage)`%) (Figure 2B). `r filter(blind, method_blind == "Never or almost never") %>% pull(percentage)`% reported that they never or almost never blind the data analyst (Figure 2C). Almost all respondents answered that they use both exploratory (`r exploratory`%) and confirmatory (`r confirmatory`%) analyses at least sometimes (Figure 2D-E).

```{r methodPlot, warning=FALSE, fig.cap="Caption goes here...", fig.align="center", out.width="100%", fig.width=11, fig.height=4.5, fig.path='figs/', dev=c('png', 'pdf')}
# Used methods figures
method_plot_data <-
  processed %>%
  select(starts_with("method_")) %>%
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "scale",
  ) %>%
  separate(variable, into = c("name_prefix", "type")) %>%
  group_by(type) %>%
  count(scale) %>%
  ungroup() %>%
  replace_na(list(scale = "Missing")) %>%
  mutate(
    scale = factor(scale, levels = c(
      "Never or almost never",
      "Sometimes",
      "About half the time",
      "Most of the time",
      "Always or almost always",
      "Missing",
      "I don't understand the question"
    )),
    type = case_when(
      type == "blind" ~ "Blind the data analyst",
      type == "confirmatory" ~ "Contain confirmatory analysis",
      type == "exploratory" ~ "Contain exploratory analysis",
      type == "preregistered" ~ "Are preregistered",
      type == "script" ~ "Share analysis scripts",
    ),
    type = factor(type, levels = c(
      "Contain exploratory analysis",
      "Contain confirmatory analysis",
      "Blind the data analyst",
      "Share analysis scripts",
      "Are preregistered"
    ))
  ) %>%
  group_by(type) %>%
  tidyr::complete(scale, fill = list(n = 0)) %>%
  mutate(
    percentage = n / sum(n)
  ) %>%
  ungroup()

@@

@@

`r pull(filter(willing, support == "positive"), percentage)`% of respondents agreed (versus `r pull(filter(willing, support == "negative"), percentage)`% who disagreed) that they would be less willing to use ALSPAC data if they were required to use an ECAW (Figure 3). `r pull(filter(opt, support == "positive"), percentage)`% agreed (`r pull(filter(opt, support == "negative"), percentage)`% disagreed) that they would opt-in if ALSPAC ran a study on ECAWs. `r pull(filter(study, support == "positive"), percentage)`% agreed (`r pull(filter(study, support == "negative"), percentage)`% disagreed) that ALSPAC should run a study on ECAWs. `r pull(filter(prefer, support == "positive"), percentage)`% agreed (`r pull(filter(prefer, support == "negative"), percentage)`% disagreed) that they would prefer using an ECAW than using typical preregistration.

```{r alspacPlot, warning=FALSE, message=FALSE, fig.cap="Caption goes here...", fig.align="center", out.width="100%", fig.width=14, fig.height=5, fig.path='figs/', dev=c('png', 'pdf')}
# Check if there is any missing and don't understand responses separately
alspac_missing_text <-
  processed %>%
  select(contains("alspac_")) %>%
  pivot_longer(
    cols = everything(),
    names_to = "item",
    values_to = "value"
  ) %>%
  dplyr::filter(is.na(value) | value == "I don't understand the question" | value == "Unsure") %>%
  mutate(item = str_to_title(str_remove(item, "^[^_]*_"))) %>%
  replace_na(list(value = "Missing")) %>%
  group_by(item, value) %>%
  summarise(
    n = n()
  ) %>%
  ungroup() %>%
  mutate(text = paste(value, "=", n))

@@

# Create figure
plot(alspac_plot_likert_data, digits = 1, ordered = TRUE, text.size = 6) +
  # TODO: have to check if this is not messing with the results
  scale_x_discrete(labels = function(x) str_wrap(x, width = 30), limits = rev(names(alspac_plot_data))) +
  scale_y_continuous(labels = c("100%", "50%", "0%", "50%", "100%"), limits = c(-105, 105)) +
  labs(title = "Thinking about a study you may run with ALSPAC data (or one that you have recently run)...") +
  theme(
    axis.title.x = element_blank(),
    title = element_text(size = 15.5),
    axis.text.y = element_text(size = 14),
    axis.text.x = element_text(size = 16),
    legend.text = element_text(size = 15),
    legend.title = element_blank()
  )
```

>>>>

Most respondents agreed that studies that analyze preexisting observational datasets are trustworthy[^3] (`r pull(filter(typically_trustworthy, support == "positive"), percentage)`%; `r pull(filter(typically_trustworthy, support == "positive"), n)`/`r pull(filter(typically_trustworthy, support == "positive"), n_sum)`) and reproducible[^4] (`r pull(filter(typically_reproducible, support == "positive"), percentage)`%; `r pull(filter(typically_reproducible, support == "positive"), n)`/`r pull(filter(typically_reproducible, support == "positive"), n_sum)`) (Figure 2, top panel). At the same time, many agreed that a study using an ECAW would be _more_ trustworthy (`r pull(filter(ecaw_trustworthy, support == "positive"), percentage)`%; `r pull(filter(ecaw_trustworthy, support == "positive"), n)`/`r pull(filter(ecaw_trustworthy, support == "positive"), n_sum)`) and _more_ reproducible (`r pull(filter(ecaw_reproducible, support == "positive"), percentage)`%; `r pull(filter(ecaw_reproducible, support == "positive"), n)`/`r pull(filter(ecaw_reproducible, support == "positive"), n_sum)`) compared to a typical study using preexisting observational data (Figure 2, bottom panel).

```{r typicallyEcawPlot, warning=FALSE, fig.cap="(ref:typicallyEcawPlotCaption)", fig.align="center", out.width="100%", fig.width=12.8, fig.height=6, fig.path='figs/', dev=c('png', 'pdf')}
# Create typically trustworthy and reproducible plot
# Check if there is any missing and don't understand responses separately
# processed %>%
#   select(contains("typically_")) %>%
#   dplyr::filter(is.na(typically_reproducible) | is.na(typically_trustworthy) | typically_reproducible == "I don't understand the question" | typically_trustworthy == "I don't understand the question") %>%
#   nrow()

@@

# Create ecaw trustworthy and reproducible plot
# Calculate missing responses
ecaw_missing <-
  processed %>%
  select(contains("ecaw_")) %>%
  pivot_longer(
    cols = everything(),
    names_to = "item",
    values_to = "value"
  ) %>%
  dplyr::filter(is.na(value) | value == "I don't understand the question") %>%
  mutate(item = str_to_title(str_remove(item, "^[^_]*_"))) %>%
  replace_na(list(value = "Missing")) %>%
  group_by(item, value) %>%
  summarise(
    n = n()
  )

@@

(ref:typicallyEcawPlotCaption) __Responses to the survey questions on trustworthiness and reproducibility of observational research with preexisting data and ECAWs.__ The survey defined trustworthy as “meaning that the results and conclusions of the publications are valid, reliable, rigorous, and accurate. That they merit trust”. The survey defined reproducible “in the sense that other researchers re-analysing the data with the same research question would produce similar results.” For each item, the number to the left of the data bar indicates the combined percentage for the responses depicted in any shade of brown/orange. The number in the center of the data bar (gray) indicates the percentage of neutral responses. The number to the right of the data bar indicates the combined percentage for the responses depicted in any shade of green. For the bottom panel we excluded the missing responses (n = `r pull(filter(ecaw_missing, item == "Trustworthy" & value == "Missing"), n)`; `r pull(filter(ecaw_missing, item == "Reproducible" & value == "Missing"), n)`) and responses of “I don't understand the question” (n = `r pull(filter(ecaw_missing, item == "Trustworthy" & value == "I don't understand the question"), n)`; `r pull(filter(ecaw_missing, item == "Reproducible" & value == "I don't understand the question"), n)`).

```{r methodDescriptives, include=FALSE}
# Define the response level order for these variables
method_levels <- c(
  "Never or almost never",
  "Sometimes",
  "About half the time",
  "Most of the time",
  "Always or almost always",
  "I don't understand the question",
  "Missing"
)

# Calculate the fequency and proportion of responses for each response level
confirmatory <- level_percentage(
  processed,
  method_confirmatory,
  method_levels,
  exclude_missing = FALSE
) %>%
  filter(method_confirmatory %in% c("Sometimes", "About half the time", "Most of the time", "Always or almost always")) %>%
  summarise(
    n = sum(n),
    # Since n_sum should be the same for the whole dataset we can use unique to return one value
    n_sum = unique(n_sum),
    percentage = sum(percentage))

exploratory <- level_percentage(
  processed,
  method_exploratory,
  method_levels,
  exclude_missing = FALSE
) %>%
  dplyr::filter(method_exploratory  %in% c("Sometimes", "About half the time", "Most of the time", "Always or almost always")) %>%
  summarise(
    n = sum(n),
    # Since n_sum should be the same for the whole dataset we can use unique to return one value
    n_sum = unique(n_sum),
    percentage = sum(percentage))

preregistered <- level_percentage(
  processed,
  method_preregistered,
  method_levels,
  exclude_missing = FALSE
)

blind <- level_percentage(
  processed,
  method_blind,
  method_levels,
  exclude_missing = FALSE
)

script <- level_percentage(
  processed,
  method_script,
  method_levels,
  exclude_missing = FALSE
)
```

Over half of respondents reported that their studies using preexisting observational data are preregistered never or almost never (`r filter(preregistered, method_preregistered == "Never or almost never") %>% pull(percentage)`%; `r filter(preregistered, method_preregistered == "Never or almost never") %>% pull(n)`/`r filter(preregistered, method_preregistered == "Never or almost never") %>% pull(n_sum)`), or sometimes (`r filter(preregistered, method_preregistered == "Sometimes") %>% pull(percentage)`%; `r filter(preregistered, method_preregistered == "Sometimes") %>% pull(n)`/`r filter(preregistered, method_preregistered == "Sometimes") %>% pull(n_sum)`) (Figure 2A). About half reported sharing their analysis scripts never or almost never (`r filter(script, method_script == "Never or almost never") %>% pull(percentage)`%; `r filter(script, method_script == "Never or almost never") %>% pull(n)`/`r filter(script, method_script == "Never or almost never") %>% pull(n_sum)`), or sometimes (`r filter(script, method_script == "Sometimes") %>% pull(percentage)`%; `r filter(script, method_script == "Sometimes") %>% pull(n)`/`r filter(script, method_script == "Sometimes") %>% pull(n_sum)`) (Figure 3). `r filter(blind, method_blind == "Never or almost never") %>% pull(percentage)`% (`r filter(blind, method_blind == "Never or almost never") %>% pull(n)`/`r filter(blind, method_blind == "Never or almost never") %>% pull(n_sum)`) reported that they never or almost never blind the data analyst (Figure 3). Almost all respondents answered that they use both exploratory (`r pull(exploratory, percentage)`%; `r pull(exploratory, n)`/`r pull(exploratory, n_sum)`) and confirmatory (`r pull(confirmatory, percentage)`%; `r pull(confirmatory, n)`/`r pull(confirmatory, n_sum)`) analyses at least sometimes (Figure 3).

```{r methodPlot, warning=FALSE, fig.cap="(ref:methodPlotCaption)", fig.align="center", out.width="100%", fig.width=11, fig.height=4.5, fig.path='figs/', dev=c('png', 'pdf')}
# Used methods figures
method_plot_data <-
  processed %>%
  select(starts_with("method_")) %>%
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "scale",
  ) %>%
  separate(variable, into = c("name_prefix", "type")) %>%
  group_by(type) %>%
  count(scale) %>%
  ungroup() %>%
  replace_na(list(scale = "Missing")) %>%
  mutate(
    scale = factor(scale, levels = c(
      "Never or almost never",
      "Sometimes",
      "About half the time",
      "Most of the time",
      "Always or almost always",
      "Missing",
      "I don't understand the question"
    )),
    type = case_when(
      type == "blind" ~ "Blind the data analyst",
      type == "confirmatory" ~ "Contain confirmatory analysis",
      type == "exploratory" ~ "Contain exploratory analysis",
      type == "preregistered" ~ "Are preregistered",
      type == "script" ~ "Share analysis scripts",
    ),
    type = factor(type, levels = c(
      "Contain exploratory analysis",
      "Contain confirmatory analysis",
      "Blind the data analyst",
      "Share analysis scripts",
      "Are preregistered"
    ))
  ) %>%
  group_by(type) %>%
  tidyr::complete(scale, fill = list(n = 0)) %>%
  mutate(
    percentage = n / sum(n)
  ) %>%
  ungroup()

@@

(ref:methodPlotCaption) __Responses to survey questions about the research practices of participants.__

@@

`r pull(filter(willing, support == "positive"), percentage)`% (`r pull(filter(willing, support == "positive"), n)`/`r pull(filter(willing, support == "positive"), n_sum)`) of respondents agreed (versus `r pull(filter(willing, support == "negative"), percentage)`%; `r pull(filter(willing, support == "negative"), n)`/`r pull(filter(willing, support == "negative"), n_sum)` who disagreed) that they would be less willing to use ALSPAC data if they were required to use an ECAW (Figure 3). `r pull(filter(opt, support == "positive"), percentage)`% (`r pull(filter(opt, support == "positive"), n)`/`r pull(filter(opt, support == "positive"), n_sum)`) agreed (`r pull(filter(opt, support == "negative"), percentage)`%; `r pull(filter(opt, support == "negative"), n)`/`r pull(filter(opt, support == "negative"), n_sum)` disagreed) that they would opt-in if ALSPAC ran a study on ECAWs. `r pull(filter(study, support == "positive"), percentage)`% (`r pull(filter(study, support == "positive"), n)`/`r pull(filter(study, support == "positive"), n_sum)`) agreed (`r pull(filter(study, support == "negative"), percentage)`%; `r pull(filter(study, support == "negative"), n)`/`r pull(filter(study, support == "negative"), n_sum)` disagreed) that ALSPAC should run a study on ECAWs. `r pull(filter(prefer, support == "positive"), percentage)`% (`r pull(filter(prefer, support == "positive"), n)`/`r pull(filter(prefer, support == "positive"), n_sum)`) agreed (`r pull(filter(prefer, support == "negative"), percentage)`%; `r pull(filter(prefer, support == "negative"), n)`/`r pull(filter(prefer, support == "negative"), n_sum)` disagreed) that they would prefer using an ECAW than using typical preregistration.

```{r alspacPlot, warning=FALSE, message=FALSE, fig.cap="(ref:alspacPlotCaption)", fig.align="center", out.width="100%", fig.width=14, fig.height=5, fig.path='figs/', dev=c('png', 'pdf')}
# Check if there is any missing and don't understand responses separately
alspac_missing <-
  processed %>%
  select(contains("alspac_")) %>%
  pivot_longer(
    cols = everything(),
    names_to = "item",
    values_to = "value"
  ) %>%
  dplyr::filter(is.na(value) | value == "I don't understand the question" | value == "Unsure") %>%
  mutate(
    item = str_to_title(str_remove(item, "^[^_]*_")),
    # We reorder it by making it a factor
    item = factor(item, levels = c(
      "Less_willing",
      "Opt_in",
      "Study",
      "Prefer_ecaw"
    )),
    # By making it a factor we can complete missing levels in the data later
    value = factor(value, levels = c(
      "Missing",
      "I don't understand the question",
      "Unsure"
    ))
  ) %>%
  replace_na(list(value = "Missing")) %>%
  group_by(item, value) %>%
  summarise(
    n = n()
  ) %>% 
  # Add n = 0 if no one choose a specific factor level
  tidyr::complete(value, fill = list(n = 0))

@@

# Create figure
plot(alspac_plot_likert_data, digits = 1, text.size = 6) +
  # TODO: have to check if this is not messing with the results
  scale_x_discrete(labels = function(x) str_wrap(x, width = 30), limits = rev(names(alspac_plot_data))) +
  scale_y_continuous(labels = c("100%", "50%", "0%", "50%", "100%"), limits = c(-105, 105)) +
  labs(title = "Thinking about a study you may run with ALSPAC data (or one that you have recently run)...") +
  theme(
    axis.title.x = element_blank(),
    title = element_text(size = 15.5),
    axis.text.y = element_text(size = 14),
    axis.text.x = element_text(size = 16),
    legend.text = element_text(size = 15),
    legend.title = element_blank()
  )
```

(ref:alspacPlotCaption) __Responses to survey questions about using ECAWs.__ The 4 questions we excluded missing values (_n_ = `r pull(filter(alspac_missing, item == "Less_willing" & value == "Missing"), n)`; `r pull(filter(alspac_missing, item == "Opt_in" & value == "Missing"), n)`; `r pull(filter(alspac_missing, item == "Study" & value == "Missing"), n)`; `r pull(filter(alspac_missing, item == "Prefer_ecaw" & value == "Missing"), n)`), responses of "I don't understand the question" (_n_ = `r pull(filter(alspac_missing, item == "Less_willing" & value == "I don't understand the question"), n)`; `r pull(filter(alspac_missing, item == "Opt_in" & value == "I don't understand the question"), n)`; `r pull(filter(alspac_missing, item == "Study" & value == "I don't understand the question"), n)`; `r pull(filter(alspac_missing, item == "Prefer_ecaw" & value == "I don't understand the question"), n)`), and responses of "Unsure" (_n_ = `r pull(filter(alspac_missing, item == "Less_willing" & value == "Unsure"), n)`; `r pull(filter(alspac_missing, item == "Opt_in" & value == "Unsure"), n)`; `r pull(filter(alspac_missing, item == "Study" & value == "Unsure"), n)`; `r pull(filter(alspac_missing, item == "Prefer_ecaw" & value == "Unsure"), n)`).

### 2023-03-23 manuscript/manuscript.tex
updated manuscript based on contributor feedback and restructured the folders to deploy the interactive plot

@@

\caption{Caption goes here...}\label{fig:typicallyEcawPlot}
\end{figure}

Respondents generally agreed that studies that analyze preexisting observational datasets are trustworthy\footnote{The survey defined trustworthy as: ``meaning that the results and conclusions of the publications are valid, reliable, rigorous, and accurate. That they merit trust.''} (72\%) and reproducible\footnote{The survey defined reproducible ``in the sense that other researchers re-analysing the data with the same research question would produce similar results.''} (79\%) (Figure 1A). At the same time, many agreed that a study using an ECAW would be \emph{more} trustworthy (70\%) and \emph{more} reproducible (69\%) compared to a typical study using preexisting observational data (Figure 1B).

Over half of respondents reported that their studies using preexisting observational data are preregistered never or almost never (38\%), or sometimes (27\%) (Figure 2A). About half reported sharing their analysis scripts never or almost never (20\%), or sometimes (32\%) (Figure 2B). 79\% reported that they never or almost never blind the data analyst (Figure 2C). Almost all respondents answered that they use both exploratory (95\%) and confirmatory (92\%) analyses at least sometimes (Figure 2D-E).

@@

\caption{Caption goes here...}\label{fig:methodPlot}
\end{figure}

25\% of respondents agreed (versus 44\% who disagreed) that they would be less willing to use ALSPAC data if they were required to use an ECAW (Figure 3). 53\% agreed (20\% disagreed) that they would opt-in if ALSPAC ran a study on ECAWs. 55\% agreed (10\% disagreed) that ALSPAC should run a study on ECAWs. 45\% agreed (22\% disagreed) that they would prefer using an ECAW than using typical preregistration.

@@

\caption{Caption goes here...}\label{fig:alspacPlot}
\end{figure}

>>>>

Most respondents agreed that studies that analyze preexisting observational datasets are trustworthy\footnote{The survey defined trustworthy as: ``meaning that the results and conclusions of the publications are valid, reliable, rigorous, and accurate. That they merit trust.''} (72\%; 77/107) and reproducible\footnote{The survey defined reproducible ``in the sense that other researchers re-analysing the data with the same research question would produce similar results.''} (79\%; 84/107) (Figure 2, top panel). At the same time, many agreed that a study using an ECAW would be \emph{more} trustworthy (70\%; 71/101) and \emph{more} reproducible (69\%; 70/102) compared to a typical study using preexisting observational data (Figure 2, bottom panel).

@@

\caption{\textbf{Responses to the survey questions on trustworthiness and reproducibility of observational research with preexisting data and ECAWs.} The survey defined trustworthy as ``meaning that the results and conclusions of the publications are valid, reliable, rigorous, and accurate. That they merit trust''. The survey defined reproducible ``in the sense that other researchers re-analysing the data with the same research question would produce similar results.'' For each item, the number to the left of the data bar indicates the combined percentage for the responses depicted in any shade of brown/orange. The number in the center of the data bar (gray) indicates the percentage of neutral responses. The number to the right of the data bar indicates the combined percentage for the responses depicted in any shade of green. For the bottom panel we excluded the missing responses (n = 2; 2) and responses of ``I don't understand the question'' (n = 4; 3).}\label{fig:typicallyEcawPlot}
\end{figure}

Over half of respondents reported that their studies using preexisting observational data are preregistered never or almost never (35\%; 37/107), or sometimes (24\%; 26/107) (Figure 2A). About half reported sharing their analysis scripts never or almost never (20\%; 21/107), or sometimes (31\%; 33/107) (Figure 3). 75\% (80/107) reported that they never or almost never blind the data analyst (Figure 3). Almost all respondents answered that they use both exploratory (91\%; 98/107) and confirmatory (85\%; 92/107) analyses at least sometimes (Figure 3).

@@

\caption{\textbf{Responses to survey questions about the research practices of participants.}}\label{fig:methodPlot}
\end{figure}

25\% (26/102) of respondents agreed (versus 44\%; 45/102 who disagreed) that they would be less willing to use ALSPAC data if they were required to use an ECAW (Figure 3). 53\% (50/95) agreed (20\%; 19/95 disagreed) that they would opt-in if ALSPAC ran a study on ECAWs. 55\% (53/97) agreed (10\%; 10/97 disagreed) that ALSPAC should run a study on ECAWs. 45\% (43/95) agreed (22\%; 21/95 disagreed) that they would prefer using an ECAW than using typical preregistration.

@@

\caption{\textbf{Responses to survey questions about using ECAWs.} The 4 questions we excluded missing values (\emph{n} = 3; 3; 3; 3), responses of ``I don't understand the question'' (\emph{n} = 0; 4; 1; 1), and responses of ``Unsure'' (\emph{n} = 2; 5; 6; 8).}\label{fig:alspacPlot}
\end{figure}

### 2023-03-23 preprocessing/ecaw_raw_processed_preprocessing.Rmd
updated manuscript based on contributor feedback and restructured the folders to deploy the interactive plot

```{r}
raw <- readr::read_csv(here("data/raw/ecaw_raw_data.csv"))
```

@@

We only include full responses in the final analysis as preregistered (see the full text of the preregistration [HERE](link)). There were `r dplyr::filter(raw, !finished)` respondents who did not finish the survey.

@@

@@

```{r}
codebook <-
  read_csv(here("data/source/ecaw_221102_source_codebook.csv")) %>% 
  select(-original_var_name) %>% 
  rename(var_name = new_var_name) %>% 
  filter(var_name %in% colnames(raw))

>>>>

```{r message=FALSE}
raw <- readr::read_csv(here("data/raw/ecaw_raw_data.csv"))
```

@@

We only include full responses in the final analysis as preregistered (see the full text of the preregistration [https://osf.io/g2fw5](https://osf.io/g2fw5)). There were `r nrow(dplyr::filter(raw, !finished))` respondents who did not finish the survey.

@@

These responses will be included in an exploratory analysis that will be published in supplementary materials D.

@@

```{r message=FALSE}
codebook <-
  read_csv(here("data/source/ecaw_221102_source_codebook.csv")) %>% 
  select(-original_var_name) %>% 
  rename(var_name = new_var_name) %>% 
  filter(var_name %in% colnames(raw))
